\chapter{Conclusions}
\label{cha:conclusions}
This chapter will describe what I have learnt, what I could have improved and some final thoughts about the project.

\section{Personal development}
Before starting this project, I have not been programming in C\# nor did I have any experience in working with Unity. Every time I try a new programming language or technology, I get a confidence boost because I see I can handle the situation and the experience will be beneficial in my future career. What I wish I had done about Unity, was to check the default access modifiers, especially for methods. Also, the order of the things in the \texttt{Update} function might matter. 

An application should be designed with software design patterns in mind. This will make it more secure and it will careful consideration on behalf of the developer. 

Documentation is important since other people might need to continue your work or they might want to adjust certain parts in order to fit their purposes.

It is useful to keep a logbook of the work one is doing and to write down the problems they encounter. This will provide a retrospective about the things they have learnt or they should improve for the next application.

It is important to use suitable names at all times.

\section{Summary}

Nowadays, we have exercised using the keyboard for long periods of time, so it seems easier to control a game in this mode, but if we put more practice into playing with an EEG and properly training the Cognitiv suite, we could achieve same results with much less of an effort. \cite{moviebrain} shows it is possible to use an fMRI (functional magnetic resonance imaging) to see quite similar pictures with what the participant is seeing while watching a movie. Given this, in a relatively short period of time, brain devices may be able to read one's mind.

My personal feeling about this project is that is helped me see on my skin how design decisions affect the development of an application. At the same time, the more time passes from a bad decision, the longer it will take to fix it. I am happy to think that my next project will benefit from the lessons learnt here and I also hope the views I have provided in this report will be helpful to other people with similar circumstances.